Supplementary figures\nCapturing regeneration in models of forest dynamics

### 2023-01-24 manuscript/supplementaryRW.Rmd
updates report from ForCEEPS in supplementary

Xavier Morin

@@

@@

ForCEEPS requires monthly data, I have thus just randomized the years
given by CHELSA database to obotain a 4000-yr long time-series for each
site, with mean monthly temperature and monthly sum of precipitations.

@@

Relying on given information, I used the following relationship for
assessing Soil Field Capacity (SFC) : SFC = 8+(X-1)\*(25-8)/(5-1), in
which X is the 'soil_qual' value in the 'soil_quality_200.csv' file.

@@

I have run two kinds of simulations : - Simulations with seed rain from
a potential species list, thus independent from the actual forest
composition ("Forclim-like"), for both thresholds (7 and 10cm) -
Simulations with seed rain depending on the actual forest composition
for both thresholds (7 and 10cm) In each site, the simulation consists
of 4000 yr-long simulation of 1ha of forest (ie. 10 patches of 1000 m²),
starting from bare-ground. There was no dispersal between patches, but
the effect of the abundance of adult trees on the composition of
regeneration was considered in half of the simulations as mentioned.

@@

As requested, I have output species specific regeneration rates per
decade and per ha. More precisely, I have considered only the last 2000
years of simulations (= to ensure that pseudo-equilibrium state is
reached). I have exported the results every 10 years for the last 2000
years at the 1ha-level. My outputs thus rely on temporal variability.
Variables: - Site: numbers corresponding to the climate data file -
Sample: one per decade, for a total of 2000 years = identified from 1 to
200 - Species: name specified as requested (eg. 'fasy') - r.trees:
number of trees outcrossing the threshold (7 or 10 cm) during the
decade, for the 10 patches simulated (= 1ha), per species - r.ba: summed
basal area of the r.trees, per species - ba: summed basal area of all
trees per species at the end of the decade - dbh: threshold used And
there are thus 4 output files: Results_Forceeps_7cm.csv
Results_Forceeps_10cm.csv Results_Forceeps_feedback_7cm.csv (=
simulations with feedback of the actual species composition on the seed
rain) Results_Forceeps_feedback 10cm.csv (= simulations with feedback of
the actual species composition on the seed rain)

>>>>

Xavier Morin & François de Coligny

@@

Morin X., de Coligny F., Bugmann H., Limousin J.-M., Ourcival J.-M., Martin-StPaul N., Simioni G., Cailleret M., Prevosto B., Toïgo M., Vennetier M., Cateau E., Guillemot J. 2021. Beyond forest succession: a gap model to study ecosystem functioning and tree community composition under climate change. Functional Ecology. 35, 955-975.

Jourdan M., Dreyfus, P., Riond C., Cordonnier T., Cornet B., de Coligny F., Morin X. 2021. Managing mixed stands can mitigate severe climate change impacts on French alpine forests. Regional Environmental Change.  21, 78.

Morin X., Damestoy T., Toïgo M., Jactel H., Castagneyrol B. Meredieu C. 2020. Using forest gap models and experimental data to explore long-term effects of tree diversity on the productivity of mixed planted forests. Annals of Forest Science. 77 https://doi.org/10.1007/s13595-020-00954-0.

@@

ForCEEPS requires monthly data. A 4000-yr long time-series was obtained for each site by randomizing available years from the CHELSA database, with mean monthly temperature and monthly sum of precipitations (see 1.2.2).

@@

Soil quality is represented by a continuous value between 1 and 5, as provided (see 1.2.3) Soil Field Capacity (SFC) was assessed as follows:
SFC = 8+(X-1)*(25-8)/(5-1), in which X is the ‘soil_qual’ value in the provided ‘soil_quality_200.csv’ file.

@@

In each site, the simulation consists of 4000 yr-long simulation of 1ha of forest (ie. 10 patches of 1000 m²), starting from bare-ground. There was no dispersal between patches.
Two kinds of simulations have been carried out in each of the 200 sites. 
In a first set of simulations, regeneration dynamics was simulated with a seed rain from a potential species list, thus independent from the actual forest composition, as classically done in gap models. Under this design, a number of seedling is randomly chosen for each patch, and a species identity is randomly sorted from a potential species list (defined at the start of simulation) assigned to each seedling. Then each seedling tries to colonize the site depending on whether the suitability between species requirements and site conditions (climate, light, soil quality, browsing index).
In a second set of simulations, regeneration dynamics was simulated with a seed rain whose composition depended on the actual forest composition. Under this design, a number of seedling is randomly chosen for each patch, but the species identity is assigned according to species relative abundance (calculated across all 10 patches according to species biomass). For instance, if at year i the adult trees of species j represent 60% of the total biomass across the 10 patches, then 60% of the seedlings that try to colonize the patches at year i will belong to species j. Then, similarly to the first design, each seedling tries to colonize the site depending on whether the suitability between species requirements and site conditions.
In the two sets of simulations, simulations have been run for both thresholds for regeneration (7 and 10 cm).

@@

Outputs consisted in species specific regeneration rates per decade and per ha, by considering the last 2000 years of simulations to ensure that pseudo-equilibrium state is reached. Results were aggregated for every 10 years for the last 2000 years at the 1ha-level. Variables:
-	Site: numbers corresponding to the climate data file
-	Sample: one per decade, for a total of 2000 years = identified from 1 to 200
-	Species: name specified as requested (eg. ‘fasy’)
-	r.trees: number of trees outcrossing the threshold (7 or 10 cm) during the decade, for the 10 patches simulated (= 1ha), per species
-	r.ba: summed basal area of the r.trees, per species
-	ba: summed basal area of all trees per species at the end of the decade
-	dbh: threshold used
